True versus apparent shapes of astrophysical bow shocks

### 2017-03-21 papers/Paper1/sec-quadrics-observations.tex
Add figures for arc fits to MIPSGAL sources

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-r0-r0}
  \caption[]{Comparison of the bow sock sizes determined from our fits
    with those given by Kobulnicky for the MIPSGAL sources.}
  \label{fig:mipsgal-sizes}
\end{figure}

>>>>

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/0510-3-star}
  (b)\\
  \includegraphics[width=\linewidth]{figs/0506-4-star}
  (c)\\
  \includegraphics[width=\linewidth]{figs/0517-5-star}
  \caption[]{Examples of fits to the bow shock shapes of MIPSGAL sources.}
  \label{fig:mipsgal-examples}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-r0-r0}
  \caption[]{Comparison of the bow shock sizes determined from our fits
    with those given by Kobulnicky for the MIPSGAL sources.}
  \label{fig:mipsgal-sizes}
\end{figure}
